### 2020-05-28 serial.tex
dropcap

@@

Generation intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
They are often used interchangeably, leading to ongoing misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
Generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias the estimate.
This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.

\section*{Significance}

>>>>

\usepackage{lettrine}

\newcommand{\dropcapfont}{\fontfamily{lmss}\bfseries\fontsize{26pt}{28pt}\selectfont}
\newcommand{\dropcap}[1]{\lettrine[lines=2,lraise=0.05,findent=0.1em, nindent=0em]{{\dropcapfont{#1}}}{}}

@@

\dropcap{G}eneration intervals and serial intervals are critical quantities for characterizing outbreak dynamics.
Generation intervals characterize the time between infection and transmission; whereas serial intervals characterize the time between the onset of symptoms in a chain of transmission.
They are often used interchangeably, leading to ongoing misunderstanding of how to use either generation or serial intervals to establish a link between the epidemic growth rate $r$ and the reproduction number \RR.
Generation intervals provide a mechanistic link between $r$ and \RR but are harder to measure via contact tracing.
While serial intervals are easier to measure from contact tracing, recent studies suggest that the two intervals give different estimates of \RR from $r$.
We present a general framework for characterizing \emph{any} epidemiological delays based on cohorts (i.e., a group of individuals that share the same event time, such as symptom onset) and show that \emph{forward-looking} serial intervals, which correctly estimates \RR from $r$, are not the same as ``intrinsic'' serial intervals, but instead change with $r$.
We provide a heuristic method for addressing potential biases that can arise from not accounting for changes in serial intervals across cohorts and apply the method to estimating \RR for the COVID-19 outbreak in China using serial interval data --- our analysis shows that using incorrectly defined serial intervals can severely bias the estimate.
This study demonstrates the importance of early epidemiological investigation through contact tracing and provides a rationale for reassessing generation intervals, serial intervals, and \RR\ estimates, for COVID-19.

\section*{Significance Statement}
